Transfer of Value Functions via Variational Methods

### 2018-05-18 NIPS 2018/main.tex
Removed todos

Thus, bounding this quantity reduces to bounding $\abs{\max_{a}Q^*(s,a) - \mm_{a}Q^*(s,a)}$ point-wisely for any $s$. Recall that applying the mellow Bellman operator is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta_{\kappa}$ induced by $\kappa$ \cite{}\todo{Cite MM}. Thus, we can write:

@@

\begin{lemma}\label{lemma:general-bound}
Fix a task $\mathcal{M}_{\tau}$. Let $p$ be a prior distribution over weights $\bm{w}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$. Assume $\wh{\xi}$ is the minimizer of \eqref{eq:elbo} for a dataset $D$ of $N$ i.i.d. samples where state-action couples are distributed according to $\nu$. Define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt B_{\bm{w}}\right]\right]$. Then, for any $\delta > 0$, with probability at least $1-\delta$:\todo{Make sure that the constants multiplying sqrt are correct now}
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align*}
\end{lemma}
\begin{proof}
Let us use Lemma \ref{lemma:l2} for the specific choice $q=q_{\wh{\xi}}$. From Eq. \eqref{eq:lemma2-1}, we have:
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] - \mathbb{E}_{q_{\wh{\xi}}}\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ =\ & \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}},
\end{align*}
where the second inequality holds since $v(\bm{w}) > 0$, while the equality holds from the definition of $\wh{\xi}$. We can now use Eq. \eqref{eq:lemma2-2} to bound $\mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right]$, thus obtaining:
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align*}
This concludes the proof.
\end{proof}

>>>>

Thus, bounding this quantity reduces to bounding $\abs{\max_{a}Q^*(s,a) - \mm_{a}Q^*(s,a)}$ point-wisely for any $s$. Recall that applying the mellow Bellman operator is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta_{\kappa}$ induced by $\kappa$ \cite{asadi2017alternative}. Thus, we can write:

@@

\begin{lemma}\label{lemma:general-bound}
Fix a task $\mathcal{M}_{\tau}$. Let $p$ be a prior distribution over weights $\bm{w}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$. Assume $\wh{\xi}$ is the minimizer of \eqref{eq:elbo} for a dataset $D$ of $N$ i.i.d. samples where state-action couples are distributed according to $\nu$. Define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt B_{\bm{w}}\right]\right]$. Then, for any $\delta > 0$, with probability at least $1-\delta$:
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align*}
\end{lemma}
\begin{proof}
Let us use Lemma \ref{lemma:l2} for the specific choice $q=q_{\wh{\xi}}$. From Eq. \eqref{eq:lemma2-1}, we have:
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] - \mathbb{E}_{q_{\wh{\xi}}}\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ =\ & \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}},
\end{align*}
where the second inequality holds since $v(\bm{w}) > 0$, while the equality holds from the definition of $\wh{\xi}$. We can now use Eq. \eqref{eq:lemma2-2} to bound $\mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right]$, thus obtaining:
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align*}
This concludes the proof.
\end{proof}
